Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
logging bug

# CACHE SETTINGS - Set these to TRUE to force recalculation
force_refit_models <- TRUE  # Set to TRUE to re-fit all models
force_recalc_emmeans <- TRUE  # Set to TRUE to recalculate marginal means

# Set parameters based on mode
if (analysis_mode == "test") {
  max_imputations_to_process <- 2  # Process only 2 imputations in test mode
} else {
  max_imputations_to_process <- NULL  # Process all available imputations
}
```

@@

  # Finalize progress
  finalize_progress(progress)

>>>>

# CACHE SETTINGS - Set these to TRUE to force recalculation
force_refit_models <- FALSE  # Set to TRUE to re-fit all models
force_recalc_emmeans <- TRUE  # Set to TRUE to recalculate marginal means

# Set parameters based on mode
if (analysis_mode == "test") {
  max_imputations_to_process <- 2  # Process only 2 imputations in test mode
} else {
  max_imputations_to_process <- NULL  # Process all available imputations
}

# Initialize logging
log_file <- init_log("outcome_analysis_interaction")
```

@@
